What is an Ancestral Recombination Graph?

### 2022-01-10 paper.tex
Outline of ARG inference methods

% See
The coalescent
process~\citep{kingman1982coalescent,kingman1982genealogy,hudson1983testing,
tajima1983evolutionary}

@@

In the original (Griffiths) formulation, nodes which have multiple parents are annotated with a
*breakpoint*, representing a genomic position. The genome lying to the left of that position is then taken to come from one parent, while the genome lying to the right is taken to come from the other parent. This is an elegantly concise encoding of the parental source, and is used, for example in the ARGweaver .arg format. However, it suffers from three principal drawbacks:

@@

% HYW: should discuss the link to biology & mitosis/meiosis: a "node" is strictly a cell - it is shorthand to associate it with an "individual"

>>>>

% See https://github.com/tskit-dev/what-is-an-arg-paper/discussions/13
% for discussions on this section

The coalescent
process~\citep{kingman1982coalescent,kingman1982genealogy,hudson1983testing,
tajima1983evolutionary}

@@

In the original (Griffiths) formulation, nodes which have multiple parents are
annotated with a breakpoint, representing a genomic position. The genome
lying to the left of that position is then taken to come from one parent, while
the genome lying to the right is taken to come from the other parent. This is
an elegantly concise encoding of the parental source, and is used, for example
in the ARGweaver .arg format. However, it suffers from three principal
drawbacks:

@@

% HYW: should discuss the link to biology & mitosis/meiosis: a "node" is
% strictly a cell - it is shorthand to associate it with an "individual"

\section*{ARG inference methods}
Using the terminology developed here to classify ARGs, we review methods developed
to infer ARGs. We focus our attention on some recent methods and discuss the
properties of the ARGs inferred.

\begin{itemize}
\item Early methods \citep{hein1990reconstructing}
\item Those sampling from the coalescent with recombination
\citep{griffiths1996ancestral,kuhner2000maximum,fearnhead2001estimating},
or SMC
\citep{rasmussen2014genome}
\item Hueristic methods~\citep{song2005efficient,minichiello2006mapping,
parida2008estimating,fallon2013acg,mirzaei2016rent}
\item Discussions of the complexity of inferring ARGs (but we need to
dig into this: is this the complexity of sampling from the coalescent,
finding a ``min ARG'', or something else?
\citep{bordewich2005computational,wang2001perfect,hein1990reconstructing,song2005constructing}
\item Recent methods: Relate, tsinfer, tsdate, etc.
\end{itemize}
